Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-04 paper/main.tex
Conf name
Adjust figures for the acmsmall document class

\title{Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R}
%\titlerunning{Why Eval (in R)?}

@@

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval. Understanding why \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific; we focus on data science code written
  in R, and compare our results to previous work that analyzed web
  programming in JavaScript. Dynamic analysis of a corpus of
  \CranAllPackages libraries and \KaggleCode end-user code confirms that
  \eval is indeed in widespread use; R's \eval is more dangerous in
  some ways, and safer in others, than what was previously reported
  for JavaScript.
  %% TODO ::: Add a sentance about summarizing why users resort to
  %% eval -- Jan
\end{abstract}

@@

  \includegraphics[width=5.8cm, trim=7.5cm 0 6cm 0, clip]{calls_per_run_per_call_site}

@@

\begin{figure}[h!]
 \includegraphics[width=0.5\textwidth, trim=5.5cm 0 6cm 0, clip]{size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{figure}

@@

>>>>

\title{Why do we Eval?\\\Large A large-scale study of Eval usage in R}
%\titlerunning{Why Eval (in R)?}

@@

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval. Understanding why \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific; we focus on data science code written
  in R, and compare our results to previous work that analyzed web
  programming in JavaScript. Dynamic analysis of a corpus of
  \CranAllPackages libraries and \KaggleCode end-user code confirms that
  \eval is indeed in widespread use; R's \eval is more dangerous in
  some ways, and safer in others, than what was previously reported
  for JavaScript.
  %% TODO ::: Add a sentence about summarizing why users resort to
  %% eval -- Jan
\end{abstract}

@@

  \includegraphics[width=5.4cm, trim=5.5cm 0 5cm 0, clip]{calls_per_run_per_call_site}

@@

\begin{figure}[h!]
 \includegraphics[width=0.5\textwidth, trim=4.8cm 0 6cm 0, clip]{size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{figure}

@@

\paragraph{Kaggle}

\paragraph{Base}
